### 2011-11-04 doc/pldi2012/highlevel.tex
Final bit of text for for the high level runtime tonight

\subsection{Task Completion}
\label{subsec:cleanup}

>>>>

\subsection{Task Completion}
\label{subsec:cleanup}
We define a task to have {\em completed} once the actual code for the task has completed.
We also define a task to have {\tt terminated} once all of the operations for a task
have finished.  We can only consider a task to be terminated once all of the regions that
the task accessed reflect all the changes made by a task and its child tasks.  However,
even after a task has completed it is possible for child tasks of that task
not to have been executed or even mapped.  We describe how we handle this scenario in
section \ref{subsec:restore}.  We also describe how physical instances are garbage
collected in seciont \ref{subsec:garbage}.

The runtime needs to know the mappings for
the child tasks as it must issue restoring copy operations so that the set of regions
that the task operated on are up to date with any data generated by child tasks.

\subsubsection{Restoring Copy Operations}
\label{subsec:restore}
An underlying assumption of the mapping process is that the resulting regions that
a task access will represent the data produced by that task.  However, this may not
be true if a task has child tasks which also modify subregions of the parent task.
In order to handle this issue the runtime must compute the necessary copy operations
from child task physical instances back to the parent task's physical instances.  To
compute these copy operations, the runtime first will wait until all the child tasks
have been mapped.  The runtime then issues a close operation to the each of the parent
task's region trees.  These close operations record all of the necessary copies to
restore the parent task's regions as well as the child tasks on which these copies
are contingent.  We call these copy operations at the end of a task {\em restoring copies}.
The runtime then issues these copies with the required dependences
and marks the task terminated once the restoring copy operations are complete.

\subsubsection{Garbage Collecting Physical Instances}
\label{subsec:garbage}
In addition to cleaning up task execution, the runtime must also deal with the problem
of garbage collecting physical instances of regions.  Physical instances must be
garbage collected since they are not visible to the application and would present
a correctness problem if deleting instances was an option for the mapper.  
Garbage collecting physical instances is a challenging problem
due to both the distributed environment of the machine and the deffered execution
model.  To solve this problem we employ a two-level reference counting scheme.  We
reference count both abstract instances and as well as physical instances.

An abstract instance maintains a count of the number of tasks that have referenced 
that abstract instance, but have not yet been mapped.  An abstract instance also tracks
whether or not it is open or closed.  An abstract instance is open if it is still
a valid abstract instance in a region tree.  An abstract instance is marked closed
once it is no longer a valid abstract instance and can therefore no longer be used
by any new tasks that are registered.

When a task is mapped it notifies an abstract instance that it has been used and can
decrement its reference count.  The task mapping also notifies the abstract instance
of the specific physical instance that was used and whether or not this use invalidates
previous physical instances of the abstract instance.  The abstract instance maintains
a reference count for each physical instance of it that has been made as well as
the set that are currently valid physical instances to be used for mapping.  When a 
task terminates, it notifies the abstract instances that it used to decrement the
reference counts for the task's specific physical instances.

There are two conditions under which a physical instance can be garbage collected.  The
first condition is when a physical instance is not a valid physical instance of
an abstract instance and its reference count is zero.  This condition occurs once no
more tasks are using a physical instance and it can longer be mapped by any task.  The
second condition is when an abstract instance is both closed and has a reference count
of zero as well as the physical instance's reference count being zero.  This handles the
case when no more tasks can be set to use an abstract instance, there are no more tasks
to map to an abstract instance, and there are no current tasks using the physical
instance.

While reference counting normally doesn't allow for garbage collection of all data structures
it will always work in this case because both our tasks and our regions are organized as 
trees which ensures that it is impossible to create cyclic region references in our system.
